\nomenclature[01]{\(  L  \)}{Instantaneous luminosity of a collider.}
\nomenclature[02]{\(  L _\mathrm{int} \)}{Integrated luminosity of a collider.}
\nomenclature[03]{\(  n_b  \)}{Number of colliding bunch pairs.}
\nomenclature[04]{\(  f_\mathrm{rev}, \omega_\mathrm{rev}  \)}{Revolution frequency and angular revolution frequency of the beam.}
\nomenclature[05]{\(  N_1, N_2  \)}{Number of particles per colliding bunch.}
\nomenclature[06]{\(  \sigma_\mathrm{xing}  \)}{Transverse beam size in the crossing plane.}
\nomenclature[07]{\(  \sigma_\mathrm{xing}  \)}{Crossing angle between the colliding beams.}
\nomenclature[08]{\(  \sigma_x, \sigma_y  \)}{Horizontal and vertical rms beam size.}
\nomenclature[09]{\(  \sigma_z  \)}{Rms bunch length in meters.}
\nomenclature[10]{\(  \sigma_t  \)}{Rms bunch length in seconds.}
\nomenclature[11]{\(  \sigma_\mathrm{xing}  \)}{Transverse beam size in the crossing plane.}
\nomenclature[12]{\(  t  \)}{Time parameter.}
\nomenclature[13]{\(  s  \)}{Parameter of the position along the accelerator ring.}
\nomenclature[14]{$(x, x^\prime)$}{Horizontal co-ordinates: position and angle.} 
\nomenclature[15]{$(y, y^\prime)$}{Vertical co-ordinates: position and angle.} 
\nomenclature[16]{$(z, \delta)$}{Longitudinal co-ordinates: position and relative momentum offset. } 
\nomenclature[17]{$(p_x, p_y, p_z)$}{Particle's momentum in the horizontal, vertical and longitudinal plane respectively.} 
\nomenclature[18]{$E_0, p_0, v_0$}{Energy, momentum, and velocity of the reference particle.}
\nomenclature[19]{$\beta_0, \gamma_0$}{Relativistic beta and gamma (Lorentz factor).}
\nomenclature[20]{$e, m_p$}{Charge and rest mass of a proton.}
\nomenclature[21]{$\rho$}{Local bending radius.}
\nomenclature[22]{$i$}{Imaginary unit}
\nomenclature[23]{$b_n, \alpha_n$}{Strength of a normal and skew multiple components of $n^\mathrm{th}$ order.}
\nomenclature[24]{$k_n$}{Normalised normal multipole coefficient.} 
\nomenclature[25]{$F_L$}{Lorentz force vector.}
\nomenclature[26]{$\mathbf{F_L}$}{Lorentz force vector.}
\nomenclature[27]{$\mathbf{E}, \mathbf{B}$}{Electric and magnetic field vector.}
\nomenclature[28]{$\mathbf{v}$}{Velocity vector.}
\nomenclature[29]{$B_x, B_y$}{Horizontal and vertical components of the magnetic field.}
\nomenclature[30]{$c$}{Speed of light.}
\nomenclature[31]{$C_0$}{Circumference of the circular accelerator.}
\nomenclature[32]{$J_x, J_y$}{Horizontal and vertical actions.}
\nomenclature[33]{$\psi_x, \psi_y$}{Horizontal and vertical phase advances from $s=0$ to $s$.}
\nomenclature[34]{$\Delta \psi_u$}{Phase advance between two locations along the ring, with $u=(x,y)$ for the horizontal and vertical plane respectively.} 
\nomenclature[35]{$\alpha_u(s)$, $\beta_u(s)$, $\gamma_u(s)$}{Alpha, beta and gamma functions respectively or Twiss or Courant-Snyder parameters, with $u=(x,y)$.} 
\nomenclature[36]{$Q_x$, $Q_y$}{Horizontal and vertical betatron tunes.}
\nomenclature[37]{$Q_{x0}$, $Q_{y0}$}{Horizontal and vertical working points of an accelerator.} 
\nomenclature[38]{$\epsilon^{\mathrm{geom}}_x$, $\epsilon^{\mathrm{geom}}_y$}{Horizontal and vertical geometric emittance.} 
\nomenclature[39]{$\epsilon_x$, $\epsilon_y$}{Horizontal and vertical normalised emittance.} 
\nomenclature[40]{$s_1$, $M_u (s_1 | s_0)$}{Linear transfer matrix from the position $s_0$ to $s_1$.}
\nomenclature[41]{$D_x$, $D_y$}{Horizontal and vertical dispersion functions.}  
\nomenclature[42]{$\sigma_\delta$}{Momentum spread or rms momentum deviation.}
\nomenclature[43]{$Q_x^{(n)}$, $Q_y^{(n)}$}{Horizontal and vertical chromaticity of $n^\mathrm{th}$ order.} 
\nomenclature[44]{$Q_x^{\prime}$, $Q_y^{\prime}$}{Horizontal cand vertical hromaticity of first order.}   
\nomenclature[45]{$L_3$}{Length of an octupole magnet.}  
\nomenclature[46]{$\alpha_{xx}$, $\alpha_{yy}$, $\alpha_{xy}$}{Horizontal, vertical, and cross-term detuning coefficients, respectively.}  
\nomenclature[47]{$T_\mathrm{rev}$}{Revolution period.}
\nomenclature[48]{$f_\mathrm{RF}, \omega_\mathrm{RF}$}{Frequency and angular frequency of the main RF system of the accelerator.}
\nomenclature[49]{$V_\mathrm{RF}$}{Voltage of the main RF system of the accelerator.}
\nomenclature[50]{$h$}{Harmonic number.}
\nomenclature[51]{$\phi_s$}{The phase of the synchronous particle.}
\nomenclature[52]{$\eta_p$}{Phase slip factor.}
\nomenclature[53]{$Q_s$, $\omega_s$}{Synchrotron tune and angular synchrotron frequency respectively.}
\nomenclature[54]{$W_x(z)$, $W_y(z)$}{Horizontal and vertical wakefunctions.}
\nomenclature[55]{$W^\mathrm{const}_x(z)$, $W^\mathrm{const}_y(z)$}{Horizontal and vertical constant wakefunctions.}
\nomenclature[56]{$W^\mathrm{dip}_x(z)$, $W^\mathrm{dip}_y(z)$}{Horizontal and vertical dipolar wakefunctions.}
\nomenclature[57]{$W^\mathrm{quad}_x(z)$, $W^\mathrm{quad}_y(z)$}{Horizontal and vertical quadrupolar wakefunctions.}
\nomenclature[58]{$Z_x(\omega)$, $Z_y(\omega)$}{Horizontal and vertical impedance.}
\nomenclature[59]{$(m,l)$}{Transverse and azimuthal head-tail modes.}
\nomenclature[60]{$ \Omega_{u0} ^{(l)} $}{Complex coherent frequency shift of head-tail mode $l$, with $u=(x,y)$ denoting the horizontal and vertical plane, respectively.}
\nomenclature[61]{$\Delta \Omega_u ^{(l)} $}{Complex frequency shift of head-tail mode $l$, with $u=(x,y)$ denoting the horizontal and vertical plane respectively.}
\nomenclature[62]{$\Delta \Omega_{u, \mathrm{re}} ^{(l)}, \Delta \Omega_{u, \mathrm{im}} ^{(l)} $}{Real and imaginary part of the complex frequency shift of head-tail mode $l$, with $u=(x,y)$ denoting the horizontal and vertical plane respectively.}
\nomenclature[63]{$\omega_x, \omega_y$}{Horizontal and vertical angular betatron frequencies}
\nomenclature[64]{$\Gamma$}{Gamma function.}
\nomenclature[65]{$Z_\mathrm{eff}$}{Effective impedance.}
\nomenclature[66]{$1/\tau_u$}{Growth (+ sign) or damping (- sign) rate of the head-tail mode $l$, where $u=(x,y)$ denotes the horizontal and vertical planes, respectively.}
\nomenclature[67]{$N_\mathrm{mp}$}{Number of macroparticles used in the tracking simulations.}
\nomenclature[68]{$N_\mathrm{turns}$}{Number of turns used in the tracking simulations.}
\nomenclature[69]{$\Delta Q_u ^{(l)} $}{Coherent frequency shifts in tune units of head-tail mode $l$, with $u=(x,y)$ denoting the horizontal and vertical plane respectively.}
\nomenclature[70]{$\Delta Q_x ^\mathrm{rms},  \Delta Q_y ^\mathrm{rms} $}{Horizontal and vertical rms betatron tune spread.}
\nomenclature[70]{$q_x, q_y $}{Fractional part of the horizontal and vertical betatron tunes.}
\nomenclature[71]{$S_\theta$}{Power spectral density of dipole noise.}
\nomenclature[72]{$S_{\Delta A}$, $S_{\Delta \phi}$ }{Power spectral density of amplitude and phase noise signal.}
\nomenclature[73]{$V_\mathrm{CC}(t)$}{Crab Cavity voltage.}
\nomenclature[74]{$V_\mathrm{0, CC}$}{Peak amplitude of Crab Cavity voltage.}
\nomenclature[75]{$f_\mathrm{CC}$}{Crab Cavity frequency.}
\nomenclature[76]{$\phi_\mathrm{CC}$}{Crab Cavity phase.}
\nomenclature[77]{$\Delta A, \Delta \phi$}{Relative deviation from the nominal amplitude and deviation from the nominal phase of the Crab Cavity.}
\nomenclature[78]{$\sigma_{\Delta A}^2, \sigma_{\Delta \phi}^2$}{Total noise power of amplitude and phase noise.}
\nomenclature[79]{$I_n(x)$}{Modified Bessel function of the first kind.}
\nomenclature[80]{$C_{\Delta A}, C_{\Delta \phi}$}{Correction terms to account for the dependence of the amplitude and phase noise induced emittance growth predicted from the Mastoridis--Baudrenghien model on the bunch length.} 
\nomenclature[81]{$\sigma_\phi$}{Rms bunch length in radians.}
\nomenclature[82]{$f$}{Frequency parameter.}
\nomenclature[83]{$\mathcal{L}(f)$}{Script-ell of $f$: the standard measure for characterising instabilities in the frequency domain.}
\nomenclature[84]{$(A, \theta, d)$}{Amplitude, phase, and vertical offset parameter of the sinusoidal fitting function used in this thesis.}
\nomenclature[85]{$(P, k, \mu, \sigma)$}{Amplitude, offset, mean, and standard deviation of the Gaussian fitting function used in this thesis.}
\nomenclature[86]{$(c_0, c_1)$}{Initial value of the emittance and emittance growth rate for the polynomial fitting function used in this thesis.}
\nomenclature[87]{$d\epsilon_x/dt, d\epsilon_y/dt$}{Horizontal and vertical normalised emittance growth rates.}
\nomenclature[88]{$\tau_\mathrm{decoh}$}{Decoherence time of the betatron oscillations.}
\nomenclature[89]{$f_b$}{Frequency of the first betatron sideband.}
\nomenclature[90]{$E_b$}{Beam energy.}
\nomenclature[91]{$k_\mathrm{LOF}, k_\mathrm{LOD}$}{Normalised strength of the focusing and defocusing Landau octupole families in the Super Proton Synchrotron (SPS).}