Write introduction here and explain what you discuss in each section.
You need the frist section to introduce the dipole noise as you will apply it in the simulations.
\section{Noise}\label{sec:noise_definition}
%External noise means that it is independent of the beam itself.
In particle accelerators, a major issue of concern is the presence of external noise as it leads to transverse emittance growth, particle losses and limits the beam lifetime. Examples of noise sources are ripples in the power converter ripples which lead to fluctuations of the magnetic fields, ground motion, and various instruments in the accelerator structure such as the transverse damper and the Crab Cavities. % sofias's thesies introduction of chatper 5.
%Ripples in the power supply voltage are converted into current ripples, depending on the magnet's impedance, which eventually leads to magnetic field perturbations through the magnet's transfer function (vacuum chamber, beam screen). sofia's thesis p.95

From the various noise sources that are present in an accelerator, this thesis focuses on the dipolar noise and mainly on the CC noise. Dipolar noise is the one produced by the majority of the noise sources and is constant along the bunch, i.e. all the particles are affected the same way. % this noise is also referred to as rigid noise 
On the other hand, the way the CC noise affects the particles depends on their longitudinal position within the bunch (more details in the following paragraphs).

%Therefore, in the following the term "noise" refers to a sequence of random kicks (stochastic process) that affect the particles within a bunch by changing their transverse momentum each turn as follows.
Past studies~\cite{Lebedev:248620, Lebedev:248622, PhysRevSTAB.18.101001} have dealt with this type of noise in the context of the induced emittance growth theoretically and in simulations. It has been shown, that the noise can be modeled as a sequence of random kicks (stochastic process) that affect the particles within a bunch by changing their transverse momentum each turn as follows:
\begin{equation}\label{eq:external_noise_kicks}
    u^\prime_1 =  u^\prime_0 + \Delta u^\prime,
\end{equation}
where $u=(x,y)$ denoting the horizontal and vertical plane and $\Delta u^\prime$ is the change of the momentum due to the noise in units of rad. In this thesis the term "noise" refers to the above mentioned stochastic process.
% This approach will be used in the following. In th
% if it is dipole noise it is oftern written: Delta u = thera


\section{Crab Cavity noise and emittance growth}\label{eq:CC_noise_intro}
As already mentioned in the Introduction (Section~\ref{sec:motivation_outline}) the presence of noise in the $\CC$ low-level RF system is an issue of major concern for the HL-LHC project as it results in transverse emittance growth and subsequently in loss of luminosity. To this end, in 2015, P.~Baudrenghien and T.~Mastoridis developed a theoretical model~\cite{PhysRevSTAB.18.101001} which predicts this transverse emittance growth induced by $\CC$ noise focusing on the HL-LHC scenario. In particular, the model assumes a hadron machine, zero synchrotron radiation damping, long bunches (in the order of cm), and white RF noise (discrete spectral lines are excluded).  

\textbf{White noise}\\
In signal analysis, white noise is a random signal with the same amplitude (intensity) at all the frequencies which results in a constant power spectral density. For the computational analysis (i.e. simulation studies), the signals are sampled at a finite number of points which are called discrete-time signals. In discrete-time, the white noise can be considered as a sequence of uncorrelated random variables taken from a Gaussian distribution with zero mean and finite standard deviation. More details on the continuous and discrete time analysis and the term of the power spectral density can be found in Appendix~\ref{ch:app_B}. The definition for the standard deviation of a distribution can be found in Appendix~\ref{ch:app_A}.

It should be highlighted, that the above mentioned model is also applicable to the SPS (where the same conditions apply), where the $\CC$s will be tested before their installation in the LHC (Section~\ref{sec:motivation_outline}). % Thus, the results from the SPS $\CC$ tests can be used for scaling to the HL-LHC case.
The equations and formulas from the theoretical model that are essential for the understanding of the studies are discussed below.


\subsection{Crab Cavity amplitude and phase noise}\label{subsec:AN_PN}
The unperturbed instantaneous $\CC$ voltage euqals the one of an ideal oscillator:
\begin{equation}\label{eq:CC_voltage_t}
    V_\mathrm{CC}(t) = \CCvoltage \sin{\left ( 2 \pi \CCfrequency t \right )},
\end{equation}

where $\CCvoltage$ is the peak amplitude of the $\CC$ voltage and $\CCfrequency$ the $\CC$ frequency. Equation~\eqref{eq:CC_voltage_t} can be re-written as a function of the longitudinal position within the bunch $z$ instead of time $z$ as follows:
\begin{equation}\label{eq:CC_voltage_z}
    V_\mathrm{CC}(z) = \CCvoltage \sin{\left ( \frac{2\pi \CCfrequency}{\beta_0 c}z \right )},
\end{equation}
where $\beta_0$ is the relativistic parameter and $c$ is the speed of light. The above equation is obtained as: $z=v \cdot t \Rightarrow t=z/v=z/(\beta_0 c)$.


% source that ΔA = ΔV/V: https://www.osti.gov/servlets/purl/1846026/
% A the phase and relative amplitude noise power spectral density  (same source)

In the presence of modulations in amplitude and phase Eq.~\eqref{eq:CC_voltage_z} becomes (details in Appendix~\ref{app:Measured_noise}):
\begin{equation}\label{eq:CC_voltage_z}
    V_\mathrm{CC}(z) = \CCvoltage (1+\Delta A) \sin{\left ( \frac{2\pi \CCfrequency}{\beta_0 c}z + \Delta \phi \right )},
\end{equation}

where $\Delta \phi$ is the deviation from the nominal phase, $2\pi \CCfrequency z/(\beta_0 c)$, and will be referred to as phase noise in the following. $\Delta A = \Delta \CCvoltage / \CCvoltage$ is the relative deviation from the nominal amplitude $\CCvoltage$ and will be referred to as amplitude noise.



As follows from the analysis in Ref.~\cite{PhysRevSTAB.18.101001} and in accordance with Eq.~\eqref{eq:external_noise_kicks} the phase and amplitude noise kicks can be treated separately, and be modeled as the following kicks on the momentum: % at the location of the CC; s=s_CC. Eq.7 in ref~\cite{PhysRevSTAB.18.101001} but for not normalised co-oridnates.
% Presetnation: https://docs.google.com/presentation/d/1Jv0Es99utlZSSg25_9oplI53A5MdPDfJSjsSneRXaV8/edit#slide=id.gbb99f3cf0a_0_65
\begin{equation}\label{eq:amplitude_noise_kick}
  \textbf{\textrm{Amplitude noise:}} \  u^\prime_1 =  u^\prime_0 + A \sin{\left (  \frac{2 \pi \CCfrequency}{c \beta_0}z   \right )},
\end{equation}
\begin{equation}\label{eq:phase_noise_kick}
    \textbf{\textrm{Phase noise:}} \ u^\prime_1 =  u^\prime_0 + A \cos{\left (  \frac{2 \pi \CCfrequency}{c \beta_0}z   \right )},
\end{equation}

where $u^\prime$, with $u=(x,y)$, is the normalised transverse momentum and $z$ the longitudinal co-ordinate as defined in Eq.~\eqref{eq:particle_coordinates}, $\CCfrequency$ is the $\CC$ frequency, $c$ is the speed of light and $\beta_0$ the relativistic $\beta$. Finally, $A=\CCvoltage /(E_b \cdot \Delta A )$ or $A=\CCvoltage /(E_b \cdot \Delta \phi )$ the scaling factor for amplitude or phase noise respectively. A typicall value of $A$ that will be used in the simulations is $10^{-8}$.


- show figures from IPAC

- CC voltage signal equation 
- amplitude and phase noise (what is the assumption to treat them seperetatly)



\subsection{Emittance growth formulas}




\section{Theoretical model}\label{eq:CC_emit_growth_formulas}

%\section{Theoretical model for Crab Cavity noise induced-emittance growth}\label{eq:CC_emit_growth_formulas}

- KEKB, (references) why are they different (philippe email exchange) they are reffered here as there are the only other studies that exist for cc noise even though they are not of used. due to different particles and different nature of noise


2. Noise, reference to noise studies ... to kek. mention why they are different.\\


For a uniform noise spectrum across the betatron tune distribution, the emittance growth resulting from amplitude noise can be estimated from:
\begin{equation}\label{eq:dey_an}
    \frac{d\epsilon}{dt}  = \betaCC \left( \frac{e\VCC\frev}{2E_b}\right)^2 \!\! C_{\Delta A} (\sigma_{\phi}) \!\! \sum_{k=-\infty}^{+\infty} S_{\Delta A}[(k \pm \bar{\nu}_b \pm \bar{\nu}_s)\frev].
\end{equation}
For phase noise, the emittance growth can be estimated from:
\begin{equation}\label{eq:dey_pn}
    \frac{d\epsilon}{dt}  = \betaCC \left( \frac{e\VCC\frev}{2E_b}\right)^2 C_{\Delta \phi} (\sigma_{\phi}) \sum_{k=-\infty}^{+\infty} S_{\Delta \phi}[(k \pm \bar{\nu}_b)\frev].
\end{equation}
 In these formulas, $\betaCC$ is the beta function at the location of the CC, $\VCC$ the CC voltage, $\frev$ the revolution frequency of the beam, $E_b$ the beam energy, and $\bar{\nu}_b$ and $\bar{\nu}_s$ the mean of the betatron and synchrotron tune distribution. $S_{\Delta A}$ and $S_{\Delta \phi}$ are the power spectral densities (PSD)~\cite{b_papoulis1991probability} of the noise at all the betatron and synchrobetatron (for the amplitude noise case) sidebands. %In SI units, $S_{\Delta A}$ and $S_{\Delta \phi}$ are measured in Hz$^{-1}$ and rad$^2$Hz$^{-1}$, respectively. 
 $C_{\Delta A}$ and $C_{\Delta \phi}$ are correction terms to account for the bunch length:
\begin{align}
C_{\Delta A}(\sigma_{\phi}) = ~& e^{-\sigma_{\phi}^2}\sum_{l=0}^{+\infty} I_{2l+1}(\sigma_{\phi}^2),\\
C_{\Delta \phi}(\sigma_{\phi}) = ~& e^{-\sigma_{\phi}^2} \left[I_0(\sigma_{\phi}^2) + 2 \sum_{l=1}^{+\infty} I_{2l}(\sigma_{\phi}^2) \right],
\end{align}
with $\sigma_{\phi}$ the rms bunch length (in radians) with respect to the CC frequency $\fCC$, and $I_n(x)$ the modified Bessel function of the first kind. 


You need to described how they are modeled in pyheadtail.
% https://docs.google.com/presentation/d/1Jv0Es99utlZSSg25_9oplI53A5MdPDfJSjsSneRXaV8/edit#slide=id.gbb99f3cf0a_0_65
$\symc$
$\symE$


\section{Modelling of phase and amplitude noise in simulations}

